---
title: "Descriptive Statistics"
author: "Amy Maldonado"
output: github_document
---

## Libraries & Packages
Install these packages and load these libraries in order to run the rest of the code.
```{r setup, include=FALSE, echo=FALSE, warning=FALSE}

knitr::opts_chunk$set(echo = TRUE)
#If you have never used these libraries before make sure to install the packages before loading the libraries
#install.packages("tidyverse")
#install.packages("epiDisplay")
#install.packages("sjPlot")
#install.packages("tidymodels")
library(tidyverse)
library(haven)
library(epiDisplay)
library(dplyr)
library(sjPlot)
library(MASS)
library(tidymodels)

```

## Loading and tidying the data
Load the predictor and outcome variables into an object (***survey***), load the sociodemographic variables into an object (***atp_w49***), rename columns (variables), recode Likert scale values to binary outcomes (0 = no, 1= yes) and refused (99) as a missing value (NA). 
```{r load_po}

pred_out <- read_sav("ATP W49.sav")%>%
  #selecting predictor, and outcome variables 
  dplyr::select("UNDERSTANDCO_W49", "PRIVACYNEWS1_W49", "CONTROLCO_W49", "PP4_W49", "CONCERNCO_W49", "GOVREGV1_W49", "BENEFITCO_W49", "POSNEGCO_W49")%>%
  #renaming 
  rename(understand=UNDERSTANDCO_W49,
         news=PRIVACYNEWS1_W49,
         control=CONTROLCO_W49,
         policy=PP4_W49,
         concern=CONCERNCO_W49,
         government=GOVREGV1_W49,
         benefit=BENEFITCO_W49,
         risk=POSNEGCO_W49)
```

```{r recode_risk}

#recode risk
pred_out1 <- pred_out %>%
  dplyr::select("risk")

#recoding variables to binary outcomes
pred_out1[pred_out1==1]<-0
pred_out1[pred_out1==2]<-1
pred_out1$index <- 1:nrow(pred_out1)

```

```{r recode_gov}

#recode gov
pred_out2 <- pred_out %>%
  dplyr::select("government")

#recoding variables to binary outcomes
pred_out2[pred_out2==2]<-0
pred_out2[pred_out2==3]<-0
pred_out2$index <- 1:nrow(pred_out2)

```

```{r recode_all}

#recoding variables to binary outcomes
pred_out[pred_out==2]<-1
pred_out[pred_out==3]<-0
pred_out[pred_out==4]<-0

#adding index column to combine dataframes
pred_out$index <- 1:nrow(pred_out)

#combining dataframes
pred_out<- merge(pred_out1, pred_out, by="index")%>%
  dplyr::select(-c(risk.y, government))%>%
  rename(`risk` = risk.x)

#combining dataframes
pred_out<- merge(pred_out2, pred_out, by="index")

#return dataframe 
pred_out

```


```{r load_s}

socio <- read_sav("ATP W49.sav")%>%
  #selecting sociodemographic variables 
  dplyr::select("F_ACSWEB", "F_INCOME_RECODE", "F_EDUCCAT", "F_AGECAT", "F_SEX")%>%
  #renaming variables
  rename(internet= F_ACSWEB,
         income=F_INCOME_RECODE,
         education=F_EDUCCAT,
         age=F_AGECAT,
         sex=F_SEX)

#adding index column to join with "survey"
socio$index <- 1:nrow(socio)

#returning dataframe
socio

```

```{r final_df}

#joining both dataframes
atp_w49 <- merge(socio, pred_out, by="index")%>%
  dplyr::select(-c(index))

#recoding "refused" variables from 99 to NA
atp_w49[atp_w49==99]<-NA

#return final dataframe
atp_w49

```


```{r ordered_v}

#ordering variables for regression models later

#predictor/independent
atp_w49$understand <- as.ordered(atp_w49$understand)
atp_w49$news <- as.ordered(atp_w49$news)
atp_w49$control <- as.ordered(atp_w49$control)
atp_w49$policy <- as.ordered(atp_w49$policy)

#outcome/dependent
atp_w49$government <- as.ordered(atp_w49$government)
atp_w49$benefit <- as.ordered(atp_w49$benefit)
atp_w49$risk <- as.ordered(atp_w49$risk) #bi
atp_w49$concern <- as.ordered(atp_w49$concern)

#covariates
atp_w49$age <- as.ordered(atp_w49$age)
atp_w49$sex <- as.ordered(atp_w49$sex) #bi
atp_w49$income <- as.ordered(atp_w49$income)
atp_w49$education <- as.ordered(atp_w49$education)
atp_w49$internet <- as.ordered(atp_w49$internet) #bi

```

## Univariate Descriptive Statistics
Frequencies of predictor, outcome, and sociodemographic variables in the dataset.
```{r predictor_univariate}

#predictor variables
understand_freq<- tab1(atp_w49$understand, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
understand_freq

news_freq<- tab1(atp_w49$news, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
news_freq

control_freq<- tab1(atp_w49$control, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
control_freq

policy_freq<- tab1(atp_w49$policy, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
policy_freq

```
* Almost half of survey respondents said they know very little about what the companies are doing with the data they collect. (*understand*, 48.8%)
* A little over half of survey respondents say they think they have very little control over the data companies collect about them. (*control*, 53.1%)

```{r outcome_univariate}
#outcome variables
concern_freq<- tab1(atp_w49$concern, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
concern_freq

government_freq<- tab1(atp_w49$government, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
government_freq

benefit_freq<- tab1(atp_w49$benefit, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
benefit_freq

risk_freq<- tab1(atp_w49$risk, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
risk_freq

```

```{r covariate_univariate}
#covariates
age_freq<- tab1(atp_w49$age, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
age_freq

sex_freq<- tab1(atp_w49$sex, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
sex_freq

income_freq<- tab1(atp_w49$income, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
income_freq

education_freq<- tab1(atp_w49$education, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
education_freq

internet_freq<- tab1(atp_w49$internet, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
internet_freq

```
* The majority of respondents believe there should be more regulation of what companies can do with their customers' personal information (*government*, 77.4%)
* Almost half of respondents said they benefit very little from the data companies collect on them (*benefit*, 49.8%)
* The majority of respondents said that the potential risks of companies collecting data outweigh the benefits (*risk*, 83.2%).

## Bivariate Descriptive Statistics
Relationships between the predictor and outcome variables in the dataset.
```{r concern_bivariate}

###outcome=concern###

#understand vs concern
understand_concern <- sjPlot::tab_xtab(var.row = atp_w49$understand, var.col = atp_w49$concern, title = "Understand vs Concern", show.row.prc = TRUE)
understand_concern

#news vs concern
news_concern <- sjPlot::tab_xtab(var.row = atp_w49$news, var.col = atp_w49$concern, title = "News vs Concern", show.row.prc = TRUE)
news_concern

#control vs concern
control_concern <- sjPlot::tab_xtab(var.row = atp_w49$control, var.col = atp_w49$concern, title = "Control vs Concern", show.row.prc = TRUE)
control_concern

#policy vs concern
policy_concern <- sjPlot::tab_xtab(var.row = atp_w49$policy, var.col = atp_w49$concern, title = "Policy vs Concern", show.row.prc = TRUE)
policy_concern
```

```{r government_bivariate}

####outcome=government###

#understand vs government
understand_government <- sjPlot::tab_xtab(var.row = atp_w49$understand, var.col = atp_w49$government, title = "Understand vs Government", show.row.prc = TRUE)
understand_government

#news vs government
news_government <- sjPlot::tab_xtab(var.row = atp_w49$news, var.col = atp_w49$government, title = "News vs Government", show.row.prc = TRUE)
news_government

#control vs government
control_government <- sjPlot::tab_xtab(var.row = atp_w49$control, var.col = atp_w49$government, title = "Control vs Government", show.row.prc = TRUE)
control_government

#policy vs government
policy_government <- sjPlot::tab_xtab(var.row = atp_w49$policy, var.col = atp_w49$government, title = "Policy vs Government", show.row.prc = TRUE)
policy_government

```

```{r benefit_bivariate}

###outcome=benefit###

#understand vs benefit
understand_benefit <- sjPlot::tab_xtab(var.row = atp_w49$understand, var.col = atp_w49$benefit, title = "Understand vs Benefit", show.row.prc = TRUE)
understand_benefit

#news vs benefit
news_benefit <- sjPlot::tab_xtab(var.row = atp_w49$news, var.col = atp_w49$benefit, title = "News vs Benefit", show.row.prc = TRUE)
news_benefit

#control vs benefit
control_benefit <- sjPlot::tab_xtab(var.row = atp_w49$control, var.col = atp_w49$benefit, title = "Control vs Benefit", show.row.prc = TRUE)
control_benefit

#policy vs benefit
policy_benefit <- sjPlot::tab_xtab(var.row = atp_w49$policy, var.col = atp_w49$benefit, title = "Policy vs Benefit", show.row.prc = TRUE)
policy_benefit
```

```{r risk_bivariate}

###outcome=risk###

#understand vs risk
understand_risk <- sjPlot::tab_xtab(var.row = atp_w49$understand, var.col = atp_w49$risk, title = "Understand vs Risk", show.row.prc = TRUE)
understand_risk

#news vs risk
news_risk <- sjPlot::tab_xtab(var.row = atp_w49$news, var.col = atp_w49$risk, title = "News vs Risk", show.row.prc = TRUE)
news_risk

#control vs risk
control_risk <- sjPlot::tab_xtab(var.row = atp_w49$control, var.col = atp_w49$risk, title = "Control vs Risk", show.row.prc = TRUE)
control_risk

#policy vs risk
policy_risk <- sjPlot::tab_xtab(var.row = atp_w49$policy, var.col = atp_w49$risk, title = "Policy vs Risk", show.row.prc = TRUE)
policy_risk

```
* Regardless of how much social media users *understand* or feel in *control* over what companies do with their data, follow *news* on privacy issues, or understand *privacy policies*, the majority of survey respondents believe there should be more government regulation of what companies can do with their customers' personal information (*government*) and that the potential risks of companies collecting data outweigh the benefits (*risk*).
* Policy vs Risk and Policy vs Government were the only bivariate relationships that were not statistically significant. (p>0.05)

## Multivariate Regression Models


Logistic Regression

```{r logit_concern}

#outcome=concern
model <- glm(concern ~ understand + control + news + policy, data = atp_w49, family = "binomial")

summary(model)

```

```{r logit_government}

#outcome=government
model <- glm(government ~ understand + control + news + policy, data = atp_w49, family = "binomial")

summary(model)

```

```{r logit_benefit}

#outcome=benefit
model <- glm(benefit ~ understand + control + news + policy, data = atp_w49, family = "binomial")

summary(model)

```


```{r logit_risk}

#outcome=risk
model <- glm(risk ~ understand + control + news + policy, data = atp_w49, family = "binomial")

summary(model)

```

```{r logit_control_concern}

#outcome=concern w/ control
model <- glm(concern ~ sex + education + income + education + internet + understand + control + news + policy, data = atp_w49, family = "binomial")

summary(model)

```

```{r logit_control_government}

#outcome=government w/ control
model <- glm(government ~ sex + education + income + education + internet + understand + control + news + policy, data = atp_w49, family = "binomial")

summary(model)

```

```{r logit_control_benefit}

#outcome=benefit w/ controls
model <- glm(benefit ~ sex + education + income + education + internet + understand + control + news + policy, data = atp_w49, family = "binomial")

summary(model)

```

```{r logit_control_risk}

#outcome=risk w/ control
model <- glm(risk ~ sex + education + income + education + internet + understand + control + news + policy, data = atp_w49, family = "binomial")

summary(model)

```
