---
title: "Descriptive Statistics"
author: "Amy Maldonado"
output: github_document
---

## Libraries & Packages
Install these packages and load these libraries in order to run the rest of the code.
```{r setup, include=FALSE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#If you have never used these libraries before make sure to install the packages before loading the libraries
#install.packages("tidyverse")
#install.packages("epiDisplay")
#install.packages("sjPlot")
library(tidyverse)
library(haven)
library(epiDisplay)
library(dplyr)
library(sjPlot)
```

## Loading and tidying the data
Load the data into an object (*atp_w49*), select and rename columns (variables) of interest, recode refused (99) as a missing value (NA). 
```{r load}

atp_w49<- read_sav("ATP W49.sav")%>%
  #selecting sociodemographic, predictor, and outcome variables 
  dplyr::select("F_ACSWEB", "F_INCOME_RECODE", "F_PARTY_FINAL", "F_EDUCCAT", "F_AGECAT", "F_SEX", "UNDERSTANDCO_W49", "PRIVACYNEWS1_W49", "CONTROLCO_W49", "PP4_W49", "CONCERNCO_W49", "GOVREGV1_W49", "BENEFITCO_W49", "POSNEGCO_W49")%>%
  #renaming variables
  rename(internet= F_ACSWEB,
         income=F_INCOME_RECODE,
         party=F_PARTY_FINAL,
         education=F_EDUCCAT,
         age=F_AGECAT,
         sex=F_SEX,
         understand=UNDERSTANDCO_W49,
         news=PRIVACYNEWS1_W49,
         control=CONTROLCO_W49,
         policy=PP4_W49,
         concern=CONCERNCO_W49,
         government=GOVREGV1_W49,
         benefit=BENEFITCO_W49,
         risk=POSNEGCO_W49)

#recoding variables from 99 to NA
atp_w49[atp_w49==99]<-NA

```

## Univariate Descriptive Statistics
Predictor and outcome variables' frequencies in the dataset.
```{r predictor univariate}

#predictor variables
understand_freq<- tab1(atp_w49$understand, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
understand_freq

news_freq<- tab1(atp_w49$news, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
news_freq

control_freq<- tab1(atp_w49$control, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
control_freq

policy_freq<- tab1(atp_w49$policy, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
policy_freq

```
* Almost half of survey respondents said they know very little about what the companies are doing with the data they collect. (*understand*, 48.8%)
* A little over half of survey respondents say they think they have very little control over the data companies collect about them. (*control*, 53.1%)

```{r outcome univariate}
#outcome variables
concern_freq<- tab1(atp_w49$concern, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
concern_freq

government_freq<- tab1(atp_w49$government, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
government_freq

benefit_freq<- tab1(atp_w49$benefit, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
benefit_freq

risk_freq<- tab1(atp_w49$risk, sort.group = "decreasing", cum.percent = TRUE, missing = FALSE)
risk_freq

```
* The majority of respondents believe there should be more regulation of what companies can do with their customers' personal information (*government*, 77.4%)
* Almost half of respondents said they benefit very little from the data companies collect on them (*benefit*, 49.8%)
* The majority of respondents said that the potential risks of companies collecting data outweigh the benefits (*risk*, 83.2%).

## Bivariate Descriptive Statistics
Relationships between the predictor and outcome variables in the dataset.
```{r bivariate}

###outcome=concern###

#understand vs concern
understand_concern <- sjPlot::tab_xtab(var.row = atp_w49$understand, var.col = atp_w49$concern, title = "Understand vs Concern", show.row.prc = TRUE)
understand_concern

#news vs concern
news_concern <- sjPlot::tab_xtab(var.row = atp_w49$news, var.col = atp_w49$concern, title = "News vs Concern", show.row.prc = TRUE)
news_concern

#control vs concern
control_concern <- sjPlot::tab_xtab(var.row = atp_w49$control, var.col = atp_w49$concern, title = "Control vs Concern", show.row.prc = TRUE)
control_concern

#policy vs concern
policy_concern <- sjPlot::tab_xtab(var.row = atp_w49$policy, var.col = atp_w49$concern, title = "Policy vs Concern", show.row.prc = TRUE)
policy_concern

####outcome=government###

#understand vs government
understand_government <- sjPlot::tab_xtab(var.row = atp_w49$understand, var.col = atp_w49$government, title = "Understand vs Government", show.row.prc = TRUE)
understand_government

#news vs government
news_government <- sjPlot::tab_xtab(var.row = atp_w49$news, var.col = atp_w49$government, title = "News vs Government", show.row.prc = TRUE)
news_government

#control vs government
control_government <- sjPlot::tab_xtab(var.row = atp_w49$control, var.col = atp_w49$government, title = "Control vs Government", show.row.prc = TRUE)
control_government

#policy vs government
policy_government <- sjPlot::tab_xtab(var.row = atp_w49$policy, var.col = atp_w49$government, title = "Policy vs Government", show.row.prc = TRUE)
policy_government

###outcome=benefit###

#understand vs benefit
understand_benefit <- sjPlot::tab_xtab(var.row = atp_w49$understand, var.col = atp_w49$benefit, title = "Understand vs Benefit", show.row.prc = TRUE)
understand_benefit

#news vs benefit
news_benefit <- sjPlot::tab_xtab(var.row = atp_w49$news, var.col = atp_w49$benefit, title = "News vs Benefit", show.row.prc = TRUE)
news_benefit

#control vs benefit
control_benefit <- sjPlot::tab_xtab(var.row = atp_w49$control, var.col = atp_w49$benefit, title = "Control vs Benefit", show.row.prc = TRUE)
control_benefit

#policy vs benefit
policy_benefit <- sjPlot::tab_xtab(var.row = atp_w49$policy, var.col = atp_w49$benefit, title = "Policy vs Benefit", show.row.prc = TRUE)
policy_benefit


###outcome=risk###

#understand vs risk
understand_risk <- sjPlot::tab_xtab(var.row = atp_w49$understand, var.col = atp_w49$risk, title = "Understand vs Risk", show.row.prc = TRUE)
understand_risk

#news vs risk
news_risk <- sjPlot::tab_xtab(var.row = atp_w49$news, var.col = atp_w49$risk, title = "News vs Risk", show.row.prc = TRUE)
news_risk

#control vs risk
control_risk <- sjPlot::tab_xtab(var.row = atp_w49$control, var.col = atp_w49$risk, title = "Control vs Risk", show.row.prc = TRUE)
control_risk

#policy vs risk
policy_risk <- sjPlot::tab_xtab(var.row = atp_w49$policy, var.col = atp_w49$risk, title = "Policy vs Risk", show.row.prc = TRUE)
policy_risk

```
* Regardless of how much social media users *understand* or feel in *control* over what companies do with their data, follow *news* on privacy issues, or understand *privacy policies*, the majority of survey respondents believe there should be more government regulation of what companies can do with their customers' personal information (*government*) and that the potential risks of companies collecting data outweigh the benefits (*risk*).

## Multivariate 
```{r}



```
